\documentclass[a4paper,10pt,standalone]{book}
\usepackage[T1]{fontenc}
%\usepackage[utf8]{inputenc}
\usepackage{lmodern,amsmath,amsfonts,amssymb,amsthm,graphicx,color,xcolor,url,theorem,textcomp,glossaries,parskip,xlop,multicol,calculator,hyperref,tikz,fontspec,mathpazo, setspace}
%\doublespacing
%\onehalfspacing
\usepackage{unicode-math}
%\defaultfontfeatures{Numbers=Lining}
\setmainfont{xkcd Script}
\setmathfont{xkcd Script}
\usetikzlibrary{decorations.pathreplacing,calligraphy,decorations.pathmorphing,calc,positioning,intersections,external}
\tikzexternalize[prefix=figures/]
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}
\graphicspath{ {./Images/} }

\raggedright
\input{PageTemplate.tex}

\title{\textbf{Duckie}\linebreak \textit{And The Search For The Golden Goose}}
\date{}
\author{Iniyan Joseph}

\begin{document}
\maketitle
%\chapter*{Introduction}     
%\section*{Why Write this Book}

%\paragraph*{} Mathematics is an essential aspect of human life. There is a stereotype of people disliking and struggling with mathematics, which I believe is simply because we are, at a young age, often told to try to compute, rather than being challenged with fundamental questions of how to understand the world around us. 
%\section*{How to use this book}
%\paragraph*{} Learning and understanding mathematics takes more than reading this book purely for its story, but wrestling with new ideas and questions, and attempting to resolve those questions through reasoning. To this end, after reading the story on each page, have students attempt to develop an answer using their intuition and prior knowledge to build toward the correct answer. Only after they have worked towards the right answer without hints and engaged in discussion, read the solution.
%\paragraph{} Even beyond the scope of the book, encourage them to ask questions about the world around them. Reason through math in games they know and love, in stories, and in everyday life and present unintuitive problems which they can use the tools from this book and otherwise to solve in genuine scenarios. 
%\section*{Additional Resources} 
%\begin{itemize}
%\item MathForLove \url{https://mathforlove.com/}
%\item MathIsFun \url{https://www.mathsisfun.com/}
%\end{itemize}

\tableofcontents
\vfill
\pagebreak
%Introduce the story
\paragraph{} All was quiet in the goose village. The cool autumn breeze scented the air with pine, and shuffled the dry leaves across the forest floor. The sun shone brightly and warmly, casting light on the main path. To an outsider looking at the village, with the older geese talking with one another and the goslings running around playing, it would have seemed an idyllic life. Undoubtedly, it was a sort of place where parent geese could look out and feel their goslings were safe. At any other time, it would have been a pleasant evening - a tranquil picture of happiness. Yet that fall evening, there was a sense of despair in the village. Each goose knew that their quiet evenings would soon be over, and that they would have to leave for migration. 
\paragraph{} "Enough is enough." Duckie thought. For as long as he could remember, he had been afraid of the long journey. With the icy mountain peaks and vast exposing stretches of forest, the journey left him and the other geese vulnerable to the unwelcome dangers of the wilderness. The vulnerability of the long travel was compounded by the harsh environment. Duckie looked up the main road at city hall, where the goose authorities stood watching the city. 
\paragraph{} Created to protect the village from danger, the goose authorities created and enforced the rules village. To ensure the the citizens followed their rules, they created the elite corps of goose police. This system had worked for some time, but in the past years, they had abused their power. They had closed down the schools, burned the village's books, and closed off the village from the outside world. But what could he do? The goose authorities, the leaders of the village, had controlled migrations for as long as anyone in the village could remember, and he would soon have to embark on the dangerous journey.
\paragraph{} Growing up, Duckie had heard the stories of the fabled "golden goose" of legend who lived on the highest mountain. According to the stories, the golden goose would bring great change to the village. That change would in turn lead to great change, and would save the village from tyranny, and lead to an era of peace. Many geese had tried to seek her, but it was a dangerous journey, and none had ever returned. 
\paragraph{} "No. I have no choice." 
\paragraph{} Duckie thought back to his childhood. In large part, it had been a quiet life. To most people, it seemed completely average, but he had had the opportunity to find some great mentors. He thought back to the faraway place on the grassy mound, where he used to meet with the wise old goose who lived outside the village. He remembered the goose's last words before leaving for his last cold winter's migration.
\paragraph{} "Remember the legend Duckie. Remember the golden goose." 
\vfill
\pagebreak
\input{Chapters/chOne.tex}
\input{Chapters/chTwo.tex}
\input{Chapters/chThree.tex}
\input{Chapters/chFour.tex}
\input{Chapters/chFive.tex}
\input{Chapters/chSix.tex}
\input{Chapters/chSeven.tex}
\input{Chapters/chEight.tex}
\end{document}