\chapter{Calculus}

\subchapter{Average Rate of Change}
{ \paragraph{} Duckie, Maggie, and Gus began to climb the mountain. 
	\paragraph{} It was a hot day, and they felt the rivulets of sweat running around their neck and over their wings. 
	\paragraph{} Panting and sweating Maggie stopped the group - "This is ridiculous. \paragraph{} This mountain is so steep!"
	\paragraph{} Gus, more experienced with physical labor, replied "You are right, this mountain is too steep to climb".
	\paragraph{} He stopped, and the rest of the group paused. 
	\paragraph{} "Why can't we fly?".
	\paragraph{} Duckie chimed in "We need to know how fast to fly up! If not, we would run straight into the mountain!"
	
	The group had traveled p meters horizontally, and had as a result climbed up k meters vertically. How much did they climb for every meter?
}
{
}
{
}
{}
\subchapter{Instantaneous Rate of Change}{
	\paragraph{}As they continued to climb the mountain, they realized that it was not changing constantly. They were either flying too far away from the ground or running into the mountain. 
	\paragraph{} "What did we do wrong?" Duckie asked. 
	\paragraph{} "It seemed like we did it correctly before" answered Maggie, confused
	\paragraph{} The mountain snow and ice which blanketed the mountain trembled as the flew past, revealing a deep chasm. Gus, watching the events unfold, made an observation. 
	\paragraph{} Because the mountain was not straight, the speed at which the height decreased and increased stayed the same as well.
	\paragraph{} "But how make it more accurate? I mean, after all, we want to find the change at a single point - the next bit of land which we will go over."
	\paragraph{} "Yeah, that amount of horizontal change is really small. Could we 'shrink' our change in x?".
	\paragraph{} Is Duckie correct? If so, why?
}{}{}{}

\subchapter{Maxima and Minima}{
	\paragraph{} As they flew higher up the mountain, they became increasingly exhausted. Even though flying helped, it was still a steep mountain, and took a lot of effort. 
	\paragraph{} "Let's stop and rest"
	\paragraph{} "I agree, we really need to stop. But the mountain is so steep. Where is the top of the mountain? Then we can stop where it will be a flat."
	\paragraph{} "Great!"
	\paragraph{} Where are the top and bottom of the mountain?
}{}{}{}

They get to the base of the mountain \\ 
They bein climbing, and notice it is getting steeper. They have climbed $\delta y$ amounts vertically, and $\delta x $ amount horizontally. \\ 
What is average rate of change \\
They want to know about slope at each point. They can make it more accurate by having less $\delta x$. They shrink the x until it is infinitesimally small, and are able to get the slope.\\ 
Can make another function for this mountain which has the value of the slope at every point? Look at a simple case and work the way up \\
They are getting tired, and must rest. They also need to know where the golden goose is. \\
\indent They find the max and min of this function.
\pagebreak